---
title: "Assignment - 2"
author: "Eda Nur COSKUN"
date: "14 01 2021"
output: word_document
---

****
```{r include=FALSE}
library(tidyverse)
ourdata <- read_csv2("data/assignment2_data.csv")
```
### PART - 1
Take a sample of 100 observations from this data("assignment2_data.csv"), and save this sample as a new data. Answer the following questions according to this new data...

****

```{r include=FALSE}
set.seed(2016555019) 
new_data <- ourdata[sample(nrow(ourdata), 100),]
```

1. **Calculate the mean sales’ values for each color.**

```{r include=FALSE}
mean_for_color <- new_data %>% 
  group_by(Color) %>%
  summarize(Mean_Sales = mean(Sales))
```

```{r echo=FALSE}
knitr::kable(mean_for_color)
```

****

2. **Calculate the mean sales’ values for each region.**

```{r include=FALSE}
mean_for_region <- new_data %>% 
  group_by(Region) %>%
  summarize(Mean_Sales = mean(Sales))
```

```{r echo=FALSE}
knitr::kable(mean_for_region)
```

****

3. **Identify the five highest sales’ value according to date, color and region separately.**

```{r include=FALSE}
highest_sales <- new_data %>%
  group_by() %>%
  summarize(Date, Color, Region, Sales) %>% 
  arrange(desc(Sales)) %>%
  filter(row_number() == 1:5)
```

```{r echo=FALSE}
knitr::kable(highest_sales)
```

****

<br>

4. **Identify the month in which the mean sales’ value is the highest.**

```{r include=FALSE}
sep_date<-new_data %>%
  separate(Date, into = c("Day", "Month", "Year"), sep ="-")

highest_month <- sep_date %>% 
  group_by(Month) %>%
  summarize(Mean_Sales = mean(Sales)) %>%
  arrange(desc(Mean_Sales)) %>%
  filter(row_number() == 1)
```

   + The month that has the highest mean sales value is **" `r highest_month$Month` "** with **" `r highest_month$Mean_Sales` "** value.

<br>

****

5. **Plot the sales according to years.**

<br>

```{r echo=FALSE, fig.height=7, fig.width=7}
sep_date <- new_data %>%
  separate(Date, into = c("Day", "Month", "Year"), sep ="-")

ggplot(data = sep_date) +
  geom_boxplot( mapping = aes(x = Year, y = Sales, color = Year)) 
```

<br>

<br> 

### PART - 2
Answer the following questions with using the words, which are provided in stringr::words...

****

1. **Take a sample of 100 words from this data, and save this sample as a new data.**

```{r include=FALSE}
set.seed(2016555019) 
new_data <- sample(words, 100)

with_col_name <- tibble(words = new_data)
```

```{r echo=FALSE}
knitr::kable(with_col_name[1:10,])
```
...

****

2. **Find words which are starting with “a” and ending with “e”.**

```{r include=FALSE}
with_a = str_subset(new_data, "^a")

a_and_e <- tibble(a_e = str_subset(with_a, "e$"))
```

   + The word(s) that is starting with "a" and ending with "e"  is **" `r a_and_e` "**.

****

3. **Calculate the number of words which have more than 3 vowels.**

```{r include=FALSE}
num_more_three <- sum(str_count(new_data, "(a|e|i|o|u)") > 3)

logic_more_three <- tibble(
  words = new_data,
  logical = str_count(new_data, "(a|e|i|o|u)") > 3
)

more_three <- logic_more_three %>%
  group_by(words) %>%
  summarize(which(logical == TRUE))

all_words <- str_c(more_three[1] %>%
                      .[[1]], collapse = ", ")
```

   + There are **" `r  num_more_three` "** words(*`r all_words`*) that have more than 3 vowels.
   
****

4. **List the five longest word in your data.**


```{r include=FALSE}
longest <- tibble(words = new_data,
                  lengths = (str_length(new_data)))
longest_5 <- longest %>%
    arrange(desc(lengths)) %>%
    head(5)
```

```{r echo=FALSE}
knitr::kable(longest_5)
```

****

5. **Try to find word(s) which contain any of these words: age, any, day, exp, her, pro, the.**

```{r include=FALSE}
containing_words <- tibble(
  contains = str_subset(new_data, "(age|any|day|exp|her|pro|the)")
)
```

```{r echo=FALSE}
knitr::kable(containing_words)
```






























